Data_Import

### 2023-04-21 Data_Import.Rmd
Added legend title.

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  coord_polar("y",start=0)+
  theme_void()
```

>>>>

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```
